---
title: "flextable"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flextable}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(varnish)
```

# Example

```{r}
table_contents <- airquality[1:10,c(6, 1:4)]
table_contents
```

## Add column headers
The `add_headers()` function deletes the existing table header and then adds (multiple) column headers. It is a wrapper for `flextable::delete_part()` and `flextable::add_header_row()`.

```{r}
table_contents %>% 
  flextable::flextable() %>% 
  add_headers(v = list(c(NA, "Air quality"),
                       c("Day", "Ozone", "Solar.R", "Wind", "Temp")),
              c = list(c(1, 4), NULL))
```

## Apply style to a table
The `style_table()` function is used to apply an overall design to a flextable. It is recommended to use `add_headers()` (to add column headers) before applying this function.

```{r}
table_contents %>% 
  flextable::flextable() %>% 
  flextable::delete_part() %>% 
  add_headers(c("Day", "Ozone", "Solar.R", "Wind", "Temp")) %>% 
  style_table()
```

## Underline header
```{r}
table_contents %>% 
  flextable::flextable() %>% 
  add_headers(v = list(c(NA, "Air quality"),
                       c("Day", "Ozone", "Solar.R", "Wind", "Temp")),
              c = list(c(1, 4), NULL)) %>% 
  style_table() %>% 
  underline_header(j = 2)
```

## Add footnotes
```{r}
table_contents %>% 
  flextable::flextable() %>% 
  flextable::delete_part() %>% 
    flextable::add_header_row(values = c("Day", "Ozone", "Solar.R", "Wind", "Temp")) %>% 
  flextable::add_header_row(values = c("", "Air quality"),
                 colwidths = c(1, 4)) %>% 
  style_table() %>% 
  underline_header(j = 2) %>% 
  add_footnote("Daily air quality measurements in New York, May 1973.")
```

```{r}
table_contents %>% 
  flextable::flextable() %>% 
  flextable::delete_part() %>% 
    flextable::add_header_row(values = c("Day", "Ozone", "Solar.R", "Wind", "Temp")) %>% 
  flextable::add_header_row(values = c("", "Air quality"),
                 colwidths = c(1, 4)) %>% 
  style_table() %>% 
  underline_header(j = 2) %>% 
  add_footnote("Daily air quality measurements in New York, May 1973.") %>% 
  add_footnote("\u00B0F",
               i = 2, j = 5, part = "header",
               symb = marker(1))
```

## Set widths of all columns
```{r}
table_contents %>% 
  flextable::flextable() %>% 
  flextable::delete_part() %>% 
    flextable::add_header_row(values = c("Day", "Ozone", "Solar.R", "Wind", "Temp")) %>% 
  flextable::add_header_row(values = c("", "Air quality"),
                 colwidths = c(1, 4)) %>% 
  style_table() %>% 
  underline_header(j = 2) %>% 
  add_footnote("Daily air quality measurements in New York, May 1973.") %>% 
  colwidths(c(10, 23, 23, 23, 23))
```
